The polynomial representation of the type $A_{n - 1}$ rational Cherednik algebra in characteristic $p \mid n$

### 2015-05-18 formalwriteup.tex
Add todo

The rational Cherednik algebra $\HH_{\hbar, c}(\h)$ admits a $\ZZ_{\geq 0}$-graded representation on the polynomial ring $A = \Sym(\h^*)$, known as the \textit{polynomial representation}. The actions of $\Sym(\h^*)$ and $k[S_n]$ on $A$ are by left multiplication and the $S_n$ action on $\h^*$, respectively.  The action of $\Sym(\h)$ is implemented by letting $y \in \h$ act via the \textit{Dunkl operator} $D_y$ defined by
\begin{align*}
D_y(f) = \hbar \partial_y f  - \sum_{k=0}^{n-1} \sum_{l=0}^{n-1} c  \langle y, x_k-x_l \rangle \frac{(1-s_{kl}) f}{x_k - x_l},
\end{align*}
where we note that $\frac{(1-s_{kl}) f}{x_k - x_l}$ is a polynomial for $f \in A$. Explicitly, for 
\[
D_i = ,
\]
we have $D_{y_i - y_j} = D_i - D_j$.

@@

Define $g(z)=\prod_{j=0}^{n-1} (1-x_jz)$ and $F(z) =\left(\sum_{k=0}^{p-1} \binom{c}{k} (g(z)-1)^k\right)$ so that $F_i(z) = \frac{F(z)}{1-x_iz}$ and $f_i = [z^p] \frac{F(z)}{1-x_iz}$.  We now show that $f_i$ are singular vectors.
\begin{proposition}\label{prop:ann} 
The elements $f_i$ for $i=0,\dots,n-1$ singular vectors in $A$.
\end{proposition}
\begin{proof}
We must show that $f_i$ is annihilated by annihilated by $D_j-D_l$ for all $j \ne l$.

@@

>>>>

The rational Cherednik algebra $\HH_{\hbar, c}(\h)$ admits a $\ZZ_{\geq 0}$-graded representation on the polynomial ring $A = \Sym(\h^*)$, known as the \textit{polynomial representation}. The actions of $\Sym(\h^*)$ and $k[S_n]$ on $A$ are by left multiplication and the $S_n$ action on $\h^*$, respectively.  The action of $\Sym(\h)$ is implemented by letting $y \in \h$ act via the \textit{Dunkl operator} $D_y$ defined by
\begin{align*}
D_y(f) = \hbar \partial_y f  - \sum_{k=0}^{n-1} \sum_{l=0}^{n-1} c  \langle y, x_k-x_l \rangle \frac{(1-s_{kl}) f}{x_k - x_l},
\end{align*}
where we note that $\frac{(1-s_{kl}) f}{x_k - x_l}$ is a polynomial for $f \in A$. Explicitly, for 
\[
D_i = 
\]
we have $D_{y_i - y_j} = D_i - D_j$.

@@

Define $g(z)=\prod_{j=0}^{n-1} (1-x_jz)$ and $F(z) =\left(\sum_{k=0}^{p-1} \binom{c}{k} (g(z)-1)^k\right)$ so that $F_i(z) = \frac{F(z)}{1-x_iz}$ and $f_i = [z^p] \frac{F(z)}{1-x_iz}$.  We now show that $f_i$ are singular vectors.

\todo[inline]{Break up the proof into lemmas, e.g. for the value of $\frac{\partial F}{\partial z}$}

\begin{proposition}\label{prop:ann} 
The elements $f_i$ for $i=0,\dots,n-1$ are singular vectors in $A$.
\end{proposition}
\begin{proof}
We must show that $f_i$ is annihilated by annihilated by $D_j-D_l$ for all $j \ne l$.

@@

\todo[inline]{Split computations out into some lemmas on computations of $F'(z)$ and $V(z)$ which explicitly mention the hypotheses that $\sum_i m_i y_i = 0$.}
